### 2023-08-07 manuscript/manuscript.Rmd
Add email address to manuscript
Move additional file information to a separate file

^\*^ Corresponding author

@@

# Additional files

Additional file 1.csv - Table S1 -
Chemical identifiers of the compounds spiked into the urine extract.

Additional file 2.pdf - Supplementary materials and methods -
Further details outlining the materials and methods used in this article.

Additional file 3.pdf - Supplementary tables -
Supplementary tables S2, S3, S4 and S5 showing adduct, isotopic, transformation and R package benchmarking information respectively.

Additional file 4.csv - Table S6 -
The molecular formula assignments for *m/z* across all experimental matrices along with any match KEGG compound IDs.

Additional file 5.csv Table S7 -
The *m/z* features directly matched to predicted ionisation products of the spiked chemical compounds in urine.

Additional file 6.csv Table S8 -
The *m/z* features assigned to spiked chemical compounds in urine.

>>>>

^\*^ Correspondence to jsf9@aber.ac.uk

@@
